The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd
Introduction writing started

# Introduction

The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; and 6) why it is important. A reader should be able to read only the introduction and have a good idea about the research that was carried out.

Trust is a big matter in this world. Especially when you need assistance from areas that you are unfamiliar with, trust is the best thing that you can rely on. For instance, if you need a lawyer, the best thing that you can do is trust him/her/the, and be 100% honest to your lawyer. In medical field, trust directly relates to your life. We are certain that you have observed that many people have been refusing to get vaccine for COVID-19. Then, we start to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that are proved and guaranteed safety such as BCG vaccine for preventing tuberculosis. It is true that we no longer have doubts against them. However, we thought that if you move sight to developing country in 1980~1990s, situation would certainly different because of well constructed healthcare system or other reasons. This curiosty triggered us to start this research.

This paper is about children immunization reports in 1987 Thailand. Specifically how the rate differs between communities, regions, people with different education levels and religion. Along with that, its cases are divided into reports from mothers and healthcare. There clearly exists limitations and gaps that we need to fill. First, we are now in 2022. We cannot go back to the period and conduct research regarding our focus. Second, thoughts cannot be measured thoroughly.

>>>>

# Introduction
Trust is a big matter in this world. Especially when you need assistance from areas that you are unfamiliar with, trust is the best thing that you can rely on. For instance, if you need a lawyer, the best thing that you can do is trust him/her/the, and be 100% honest to your lawyer. In medical field, trust directly relates to your life. We are certain that you have observed that many people have been refusing to get vaccine for COVID-19. Then, we start to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that are proved and guaranteed safety such as BCG vaccine for preventing tuberculosis. It is true that we no longer have doubts against them. However, we thought that if you move sight to developing country in 1980~1990s, situation would certainly different because of well constructed healthcare system or other reasons. This curiosty triggered us to start this research.

This paper is about children immunization reports in 1987 Thailand. Specifically how the rate differs between communities, regions, people with different education levels and religion. Along with that, its cases are divided into reports from mothers and healthcare. There clearly exists limitations and gaps that we need to fill. First, we are now in 2022. We cannot go back to the period and conduct research regarding our focus. Second, thoughts cannot be measured thoroughly. To overcome the limitations, we tried to look for powerful candidates. Among many, we thought that 1987 DHS survey in Thailand specifically regarding children immunization rate with respect to healthcare, their mothers and the participants' features would be the best one to represent our interest.

We first had to convert pdf file to csv.After that throughout the analysis of relation between the variables and immunization rate reported by healthcare and mothers, we could observe that there existed significant gap between healthcare and mothers with respect to variables. This is an important finding because it shows that there could be lack of trust toward healthcare system or shortage of healthcare supports in Thailand. With further research after, we can observe how it has been improved since 1987, but for now we are going to focus on why. For detailed answer for why will be discussed in discussion session.

For this paper, after this introduction session, you are going to explore

2) Data
3) Results
4) Discussion
5) Reference list
